\documentclass[12pt,a4paper,oneside]{article} 
\usepackage[margin=1.0in]{geometry}

\begin{document}

\title{Cover Letter}
\author{Trevor P. Stewart}
\date{}

\maketitle

\noindent{\bf Contact Information} 
\newline
\newline
\noindent{\textit{Address} \\ 90 Charing Cres.\\Fredericton, New Brunswick\\E3B 4R7\\Canada\\
\newline
\newline  
\noindent{\textit{Phone} +1 (506) 472-1173 \\
\textit{E-mail} stewartt1982@gmail.com}
\newline
\newline

\noindent{To Whom It May Concern:}
\newline
\newline
\noindent{I am writing regarding the Robotics AI Engineer position being offered on linkedin.com by your company, Telexistence Inc.}
\newline
\newline
\noindent{My background is in both computer science (BCS) and physics (BSc, MSc, PhD).  I have spent my professional career to this point in academia, specifically in the field of experimental particle physics.  The main 3 experiments that I have worked on are as follows (details of that work on resume and academic CV):
  \begin{itemize}
  \item ZEUS experiment (DESY, Hamburg, Germany) - An electron-proton collider experiment.  Obtained both an MSc and PhD on data analyses on this experiment.
  \item T2K experiment (Tokaimura, Ibaraki/Hida, Gifu, Japan) - A neutrino oscillation experiment. 
  \item Hyper-Kamiokande (Tokaimura, Ibaraki/Hida, Gifu, Japan) - A proposed successor experiment to the existing Super-Kamiokande experiment.
  \end{itemize}
Due to this background I am proficient in advanced data analysis (using data sets in the multi-TB size range), mathematics, statistics and computing (programming, data structures, algorithms, etc.).  Due to the nature of how modern particle physics experiments collect and analyze their data, I am an experienced programmer in C/C++, Perl, Python, FORTRAN and have experience with a number of other languages.  Additionally I have gained experience in R\&D via the Hyper-Kamiokande data acquisition system, starting from scratch, to proof of concept, to a tested and functional system (though one that will likely change before being implemented in the actual Hyper-Kamiokande detector, due to the long time scale of the project).  
}
\newline
\newline
\noindent{I have recently decided to make the move from academia to private industry, primarily due to a wish for a more permanent position (particularly a position in Japan) rather than moving countries/continents every 2-3 years as a postdoctoral researcher.  Given my background in data analysis, computer science/programming, and scientific mindset, I am primarily interested in data science/analysis/engineering roles.  While many of my skills are transferable to these types of positions, I have been making a study of the python data science stack (ie. numpy, scipy, scikit-learn, tensorflow, etc).
}
\newline
\newline
\noindent{I appreciate your consideration of this application.  I may be contacted using the information supplied above. }
\newline
\newline
Sincerely,
\newline
Trevor Stewart
\newline
\newline
\noindent{\begin{itemize}
  \item Coverletter (pages 1-2)
  \item Resume (pages 3-4)
  \item Academic CV (pages 5-8)
\end{itemize}}



\end{document}
